---
title: "Essential Vocabu lary Tester"
author: "Brian Lee"
date: "April 23, 2022"
source: "Vocabulary.com (https://www.vocabulary.com/lists/145774)"
output: html_document
---

##############################################################################
#############Install & Load R Packages and Set Folder Directory###############
##############################################################################
1. Check For Installed R Packages And Install Missing Packages
2. Load R Pacakges
3. Set Import & Export Folder Directory -- Update "dir" on line 30
(e.g. dir <- "C:/Users/KT/Documents/Projects/Essential Vocabularies/")

```{r Install & Load R Pakcages and Set Folder Directory}
#1. Check For Installed R Packages And Intall Missing Packages
packages <- c("dplyr","tools")
missingpackages <- setdiff(packages, rownames(installed.packages()))
if(length(missingpackages) > 0){
  install.packages(missingpackages)
}

#2. Load R Pacakges
library(dplyr)
library(tools)

#3. Set Import & Export Folder Directory
dir <- "C:/Users/KT/Documents/Projects/Essential Vocabularies/"
```


##############################################################################
###################Import, Format and Clean Raw Data##########################
##############################################################################
1. Read In File
2. Format Import File To Have Vocabulary On Column 1 And Definition On Column 2
 2.1. Create "Definition" Column And Copy Over Definition
 2.2. Move Definition Column Up One Row So Definitions Match Vocabularies
 2.3. Check If Definitions Match Vocabularies; If They Don't Match, Print "Check Your Data"
 2.4. Delete Definitions From Column 1
 2.5. Remove Number From Column 1, Rename Column Name, Make Propercase

```{r Import, Format and Clean Raw Data}
#1. Read In File
vocab <- read.csv(paste0(dir,"EssentialVocabs.csv"),stringsAsFactors = F,header=F)

#2. Format Import File To Have Vocabulary On Column 1 And Definition On Column 2
 #2.1. Create "Definition" Column And Copy Over Definition
vocab$Definition <- NA
vocab$Definition[!grepl("\\d",vocab$V1)] <- vocab$V1[!grepl("\\d",vocab$V1)]
 #2.2. Move Definition Column Up One Row So Definitions Match Vocabularies
rownum_even <- sort(seq(2,nrow(vocab),2))
for (i in rownum_even){
  vocab$Definition[i-1] <- vocab$Definition[i]
}
 #2.3. Check If Definitions Match Vocabularies; If They Don't Match, Print "Check Your Data"
for(i in rownum_even){
  if(vocab$V1[i]!=vocab$Definition[i-1]){
    print("Check Your Data")
  }
  break
}
 #2.4. Delete Definitions From Column 1
vocab <- vocab[-rownum_even,]
 #2.5. Remove Number From Column 1, Rename Column Name, Make Propercase
vocab$V1  <-  gsub("\\d{1,3}\\.\\s","",vocab$V1)
names(vocab)[names(vocab)=="V1"]  <-  "Vocabulary"
vocab$Vocabulary<-toTitleCase(vocab$Vocabulary)


```


##############################################################################
###########################Create and Run Test################################
##############################################################################
1. Create "test" Data Frame
2. Run Actual Testing

```{r Create and Run Test}
#1. Create "test" Data Frame
test <- data.frame("Definition"=vector(),"Vocabulary"=vector(),"Answer"=vector(),"Result"=vector())

#2. Run Actual Testing -- Pick 10 Random Vocabularies Or Number of Your Choice And Test Your Input ---  To Adjust # of Vocabularies for Testing, Update Number on Line 88 (e.g. 10)
review <- data.frame("Vocabulary"=vector(),"Definition"=vector())
review1 <- data.frame("Vocabulary"=vector(),"Definition"=vector())
for(i in 1:3){
  test[i,1] <- sample(vocab$Definition,1)
  test[i,2] <- vocab$Vocabulary[vocab$Definition%in%test[i,1]]
  cat("Test #",i,". ",test[i,1],";",sep="")
  input <- readline(prompt="  Type In Your Answer:  ")
  test[i,3] <- toTitleCase(input)
  if(tolower(input)==tolower(test[i,2])){
    test[i,4] <- "Correct"  
    cat("Your answer was ",toTitleCase(test[i,3]),". It is ",test[i,4],". ",sep="")
    cat( "\n" )
  }else{
    test[i,4] <- "Incorrect"
    cat("Your answer was ",toTitleCase(test[i,3]),". It is ",test[i,4],". Correct answer is ",test[i,2],". ",sep="")
    cat( "\n" )
}
}

```


##############################################################################
##############Print Test Score And Export Misses For Review###################
##############################################################################
1. Print Test Score
2. Combine and Export Misses

```{r Print Test Score And Export Misses For Review}
#1. Print Score
score<-paste0("Your score is ",paste(round(sum(test$Result=="Correct")/nrow(test)*100,0)),"%")
print(score)

#2. Combine and Export Misses
review <- test[test$Result=="Incorrect",]
write.csv(review,paste0(dir,"MissesToReview_",Sys.Date(),".csv"),row.names = F)


```